Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-05 csf-2017/paper.tex
note added

\begin{itemize}
\item Formal model of a simple but representative capability machine with local capabilities
\item Detailed study of how to do safe stack and return pointer management in this setting, taking into account:
\begin{itemize}
\item untrusted adversary
\item higher-order code: callbacks passed to and received from the adversary
\item efficient stack management
\item no OS support
\end{itemize}
\item Logical relation for reasoning about code in this capability machine
\item Fundamental theorem that expresses the guarantees offered by a capability machine for untrusted code
\item Technical contributions: reuse existing ideas in a new way:
\begin{itemize}
\item replace biorthogonal closure by a single orthogonal closure
because assembly languages remove the distinction between the
continuation and the arguments
\end{itemize}
\end{itemize}
LB: we need to relate this carefully to Hur-Dreyer, who used
      biorthogonality even though they also worked with an assembly
      language. (If I recall correctly, they assumed some properties
      of the low level language, which is why the biortho was the
      right ting, but we need to check.)
LS: It is my impression that they were interested in the relation
between high-level and low-level programs. They are therefore in
particular interested in low-level programs compiled from high-level
programs which means that the continuation is always invoked in the 
same way. Our realisation was that anything we pass as an argument 
in a "call" can be used as a continuation, so the continuation 
relation was redundant. Eventhough we do try to give our programs
some structure using the macros, our logical relation is strong enough
to handle unstructured programs as well.
\begin{itemize}
\item STSs with public/private transitions for dealing with local capabilities: play the same role as before, but in different places of the LR.
\end{itemize}
\begin{itemize}
\item Demonstrate all of this on several examples:
\begin{itemize}
\item security examples
\item the most challenging examples from existing literature on reasoning about well-bracketed control flow in lambda calculi
\item some compartmentalisation result?
\item whatever else we do..
\end{itemize}
\end{itemize}

>>>>

\begin{itemize}
\item Formal model of a simple but representative capability machine with local capabilities
\item Detailed study of how to do safe stack and return pointer management in this setting, taking into account:
\begin{itemize}
\item untrusted adversary
\item higher-order code: callbacks passed to and received from the adversary
\item efficient stack management
\item no OS support
\end{itemize}
\item Logical relation for reasoning about code in this capability machine
\item Fundamental theorem that expresses the guarantees offered by a capability machine for untrusted code
\item Technical contributions: reuse existing ideas in a new way:
\begin{itemize}
\item replace biorthogonal closure by a single orthogonal closure
because assembly languages remove the distinction between the
continuation and the arguments
\end{itemize}
\end{itemize}
LB: I think we should have some discussion of the flexibility /
  strength of our LR.  The LR defines which computations we think of
  as well-behaved.   
 We should give simple / trivial examples of
  code not in the LR. But we may also want to emphasize that the LR is 
  not too restricting, e.g., it does not enforce a certain calling
  scheme (examplied by Example \verb!f1! which
  does not use the stack and the following examples which do use the
  stack). This ties in to the discussion of biorthogonality, see the
  following paragraphs.

LB: we need to relate this carefully to Hur-Dreyer, who used
      biorthogonality even though they also worked with an assembly
      language. (If I recall correctly, they assumed some properties
      of the low level language, which is why the biortho was the
      right ting, but we need to check.)

LS: It is my impression that they were interested in the relation
between high-level and low-level programs. They are therefore in
particular interested in low-level programs compiled from high-level
programs which means that the continuation is always invoked in the 
same way. Our realisation was that anything we pass as an argument 
in a "call" can be used as a continuation, so the continuation 
relation was redundant. Even though we do try to give our programs
some structure using the macros, our logical relation is strong enough
to handle unstructured programs as well.
\begin{itemize}
\item STSs with public/private transitions for dealing with local capabilities: play the same role as before, but in different places of the LR.
\end{itemize}
\begin{itemize}
\item Demonstrate all of this on several examples:
\begin{itemize}
\item security examples
\item the most challenging examples from existing literature on reasoning about well-bracketed control flow in lambda calculi
\item some compartmentalisation result?
\item whatever else we do..
\end{itemize}
\end{itemize}
